resistanceModelNotesAndy

### 2015-07-06 resistanceModelNotesAndy.Rmd
notes

@@

>>>>

** 6/7/15 **
`plotcurtis_f2_generic` : a function allowing mixture & individual scenarios to be compared, similar to Curtis Fig2.

In creating a shiny app to display this, I could allow user to select parameters, but then the run might take a little while because it has to do 3 runs (I1,I2,mix) & post processing. Quicker may be to display my sensitivity analysis results & allow user to step through scenarios. + include printing out the input values used (& maybe even their relative position within ranges).

@@

1. should I create a little shiny app allowing the mixture & sequential scenarios to be compared ?
